---
title: "hw 3"
author: "korede"
date: "9/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(nycflights13)
library(ggplot2)
library(tidyverse)
```

https://github.com/Uloederok/repo 

Time of day has an effect on flight delays, so choosing the right time to fly is very important.
In 2013, when flying out of New york, to avoid delays as much as possible it is recommended you pick a time early in the morning between 4:30 am and 6 am since it is at those times arrival delays are avoided the mosts. 

Delays are however affected by multiple factors, such as airline, month, and airport. Below I will present summaries and figures that better explain this.



Q) What time of day should you fly if you want to avoid delays as much as possible?

A) it is recommended you pick a time early in the morning between 4:30 am and 6 am 
```{r echo=TRUE}
(time_2fly <- flights %>% group_by(dep_time) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay))
```


Q) Does this choice depend on airline?

A) Yes, with the airline that uses the carrier code "VX" as an airline that avoids delays better than others
```{r echo=TRUE}

fly <- flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay)


flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay, carrier)


ggplot(fly, mapping = aes(month, delay)) + geom_boxplot(aes(colour = carrier)) + facet_wrap(origin~.)


```



Does this choice depend on airport? 

If you want to avoid delays as much as possible, it is best to not fly into JFK airport out of the 3 New york airports in question, since the JFK airport has the highest number of arrival delays
```{r echo=TRUE}

fly <- flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay)


flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(desc(delay, origin))


ggplot(fly, mapping = aes(month, delay)) + geom_boxplot() + facet_wrap(origin~.)

```



Does this choice depend on the month? 

If you want to avoid delays as much as possible, it is best to fly during the May
```{r echo=TRUE}

fly <- flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay)


flights %>%   group_by(month,dep_time, origin, dest, carrier) %>% 
  summarize(delay = mean(arr_delay, na.rm = T)) %>% arrange(delay, month)


ggplot(fly, mapping = aes(month, delay)) + geom_boxplot() + facet_wrap(month~.)
```


