---
title: "hw 1"
author: "korede"
date: "9/16/2021"
output: github_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(dplyr)
library(tidyverse)
bridge = read_csv("hawaii bridge.csv")
h_bridge = select(bridge, c('YEAR_BUILT_027','DECK_COND_058','STATE_CODE_001','STRUCTURE_NUMBER_008','DIRECTION_005E'))

h_bridge = h_bridge %>% rename(year = YEAR_BUILT_027, condition_rate = DECK_COND_058, fipscode = STATE_CODE_001, 
bridge_id = STRUCTURE_NUMBER_008, direction = DIRECTION_005E ) 
```

## R Markdown

include link to github in html doc
do str(data)
imake a plot 


library(rvest)
library(tidyverse)

##Import NBI DATA to excel-https://www.fhwa.dot.gov/bridge/nbi/importing.pdf; then save as csv 
bridge = read_csv("hawaii bridge.csv")
h_bridge = select(bridge, c('YEAR_BUILT_027','DECK_COND_058','STATE_CODE_001','STRUCTURE_NUMBER_008','DIRECTION_005E'))

h_bridge = h_bridge %>% rename(year = YEAR_BUILT_027, condition_rate = DECK_COND_058, fipscode = STATE_CODE_001, 
bridge_id = STRUCTURE_NUMBER_008, direction = DIRECTION_005E ) 



str(h_bridge)


plot = ggplot(data = h_bridge) + 
  geom_point(mapping = aes(x = year, y = direction, color = condition_rate))
  
print(plot)
  
plot()

print(plot)
```{r echo=TRUE}
 ggplot(data = h_bridge) + 
  geom_point(mapping = aes(x = year, y = direction, color = condition_rate))
```

